Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-10 paper.tex

\title{Msprime 1.0: an efficient and extensible coalescent simulation framework}
\author{Author list to be filled in
}
% \address{

%%Affiliations:
% Franz Baumdicker:
% Cluster of Excellence "Controlling Microbes to Fight Infections", Mathematical and Computational Population Genetics, University of Tübingen, Germany

% Consuelo D. Quinto-Cortés
%National Laboratory of Genomics for Biodiversity (LANGEBIO), Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico

% Peter L. Ralph
% Institute of Ecology and Evolution, Departments of Mathematics and Biology, University of Oregon, USA

% \author[n]{Graham Gower}
% \affil[n]{Lundbeck GeoGenetics Centre, Globe Institute, Faculty of Health and Medical Sciences, University of Copenhagen, Denmark}

>>>>

\title{Efficient ancestry and mutation simulation with msprime 1.0}
% First authors
%% FIXME affiliations are all broken
\author[1,$\star$]{Franz Baumdicker}
\author[2,$\star$]{Gertjan Bisschop}
\author[3,$\star$]{Daniel Goldstein}
\author[4,$\star$]{Graham Gower}
\author[5,$\star$]{Aaron P. Ragsdale}
\author[6,$\star$]{Georgia Tsambos}
\author[7,$\star$]{Sha Zhu}

% Middle Authors
\author[8]{Bjarki Eldon}
\author[9]{Castedo E. Ellerman}
\author[10]{Jared G. Galloway}
\author[11]{Ariella L. Gladstein}
\author[12]{Gregor Gorjanc}
\author[13]{Guo, Bing}
\author[7]{Ben Jeffery}
\author[14]{Warren W. Kretzschmar}
\author[15]{Ivan Krukov}
\author[2]{Konrad Lohse}
\author[16]{Michael Matschiner}
\author[15]{Dominic Nelson}
\author[17]{Nathaniel Pope}
\author[18]{Consuelo D. Quinto-Cort\'es}
\author[10]{Murillo F. Rodrigues}
\author[19]{Kumar Suanack}
\author[20]{Thibaut Sellinger}
\author[21]{Kevin Thornton}
\author[22]{Hugo van Kemenade}
\author[7]{Anthony W. Wohns}
\author[7]{H. Yan Wong}

% Senior Authors
\author[15,$\dagger$]{Simon Gravel}
\author[10,$\dagger$]{Andrew D. Kern}
\author[23,$\dagger$]{Jere Koskela}
\author[10,24,$\dagger$]{Peter L. Ralph}

% Corresponding
\author[7,$\ddagger$]{Jerome Kelleher}

% Franz
\affil[1]{Mathematical and Computational Population Genetics, University of T\"ubingen}
% Gertjan, Konrad
\affil[2]{Institute of Evolutionary Biology, The University of Edinburgh}
% Daniel
\affil[3]{FIXME: DANIEL'S AFFILIATION}
% Graham
\affil[4]{Lundbeck GeoGenetics Centre, Globe Institute, University of Copenhagen}
% Simon, Dom, Ivan
\affil[5]{FIXME AARON's AFFILIATION}
% Georgia
\affil[6]{Melbourne Integrative Genomics, School of Mathematics and Statistics,
    University of Melbourne}
% Jerome, Yan, Wilder, Joe
\affil[7]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
    University of Oxford}

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Department of Biology and Institute of Ecology and Evolution,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

\affil[$\star$]{Denotes shared first authorship, listed alphabetically}
\affil[$\dagger$]{Denotes shared senior authorship, listed alphabetically}
\affil[$\ddagger$]{Denotes corresponding author}
